|

### 2022-12-24 rmd/manuscript.Rmd
edit: minor

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1D**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s; the release numbers at other watersheds vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations. This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

>>>>

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of the intentional release of masu salmon (**Figure 1D**) on the long-term stability of stream fish communities in Hokkaido, Japan. In the protected watersheds (all separated by the ocean; **Figure 1C**), a long-term program exists to monitor stream fish communities along with the official release records. The release of masu salmon began in the 1950s; the release numbers vary due mainly to logistical reasons, while several of the watersheds are not subject to intentional release to preserve regional populations. This resulted in the average annual release ranging from `r round(min(df_stock_mu$mean_stock), 2)` (no release) to `r round(max(df_stock_mu$mean_stock), 2)` million fish across watersheds during 1999 -- 2019. The majority of release occurs in spring near fish survey locations, after which salmon fry stays in freshwater for at least one year with other stream fishes (see **Figure S16** for a co-occurrence matrix in our dataset). Therefore, the study system sets the stage for a "natural experiment" to test our theoretical predictions. We used the data from 1999 to 2019 at `r n_distinct(df_fish$site_id)` sites within `r n_distinct(df_fish$river)` independent watersheds (see **Methods** for selection criteria). Using hierarchical Bayesian models, we quantified the effect of intentional release on community dynamics while accounting for the potential effects of climates and local abiotic factors.

### 2022-12-24 rmd/supporting_info.Rmd
edit: minor

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \setlength{\headheight}{13.6pt}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

In the monitoring program, a two-pass sampling method was employed at all sampling sites. In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area. The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net). Thus, this sampling method has a constant sampling effort per unit area across sites.

>>>>

---
title: |
  ![](images/logo.png){width=4in}  
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath, fancyhdr, caption, booktabs}
  - \setlength{\headheight}{13.6pt}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

The monitoring program employed a two-pass sampling method at all sampling sites. In each pass, a combination of electrofishing and cast net (two-pass) was used to effectively catch both benthic and water-column species in a given area. The number of cast-net throws was determined as the sampled area divided by $4.5~\text{m}^2$ (the area covered by a cast net). Thus, this sampling method has a constant sampling effort per unit area across sites.
